---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hypatia

<!-- badges: start -->
[![R build status](https://github.com/mrc-ide/hypatia/workflows/R-CMD-check/badge.svg)](https://github.com/mrc-ide/hypatia/actions)
[![CodeFactor](https://www.codefactor.io/repository/github/mrc-ide/hypatia/badge)](https://www.codefactor.io/repository/github/mrc-ide/hypatia)
[![codecov.io](https://codecov.io/github/mrc-ide/hypatia/coverage.svg?branch=main)](https://codecov.io/github/mrc-ide/hypatia?branch=main)
<!-- badges: end -->

The goal of hypatia is to enable SQUIRE to be run on an individual basis rather than aggregate

## Installation

You can install the released version of hypatia from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("hypatia")
devtools::install_github("ggplot2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mrc-ide/hypatia")
```

and packages:

``` r
options(warn = - 1) 
library('remotes')
install_github('mrc-ide/individual')
library(individual)
```

## Example
This is an example showing how to run the simulation

```{r, simulation, echo = FALSE}
options(warn = - 1) 
 pop <- squire::get_population("Afghanistan", simple_SEIR = FALSE)

 dt <- 1
 R0 <-2 
 tt_contact_matrix <- 0
 time_period <- 1000
 newpopulation <- 10000
 timestep <- 100
 
  psq <- squire::parameters_explicit_SEEIR(
    population = pop$n,
    dt = dt,
    R0 = R0,
    tt_contact_matrix = tt_contact_matrix,
    time_period = time_period,
    contact_matrix_set = squire::contact_matrices[[1]])



```


## License

MIT © Imperial College of Science, Technology and Medicine
