---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hypatia

<!-- badges: start -->
[![R build status](https://github.com/mrc-ide/hypatia/workflows/R-CMD-check/badge.svg)](https://github.com/mrc-ide/hypatia/actions)
[![CodeFactor](https://www.codefactor.io/repository/github/mrc-ide/hypatia/badge)](https://www.codefactor.io/repository/github/mrc-ide/hypatia)
[![codecov.io](https://codecov.io/github/mrc-ide/hypatia/coverage.svg?branch=main)](https://codecov.io/github/mrc-ide/hypatia?branch=main)
<!-- badges: end -->

The goal of hypatia is to enable SQUIRE to be run on an individual basis rather than aggregate

## Installation

You can install the released version of hypatia from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("hypatia")
devtools::install_github("ggplot2")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mrc-ide/hypatia")
```

and packages:

``` r
options(warn = - 1) 
library('remotes')
install_github('mrc-ide/individual')
library(individual)
```

## Example
This is an example showing how to run the simulation

```{r, simulation, echo = FALSE}
options(warn = - 1) 
 pop <- squire::get_population("Afghanistan", simple_SEIR = FALSE)

 dt <- 1
 R0 <-2 
 tt_contact_matrix <- 0
 time_period <- 1000
 newpopulation <- 10000
 timestep <- 100
 
  psq <- squire::parameters_explicit_SEEIR(
    population = pop$n,
    dt = dt,
    R0 = R0,
    tt_contact_matrix = tt_contact_matrix,
    time_period = time_period,
    contact_matrix_set = squire::contact_matrices[[1]])

  dt <- psq$dt

  numberof_days <- 5

  beta <- squire::beta_est_explicit(psq$dur_IMild, psq$dur_ICase,
                                    psq$prob_hosp,
                                    psq$mix_mat_set[1, , ], R0 = R0)

  
  states <- hypatia:::create_states(psq)

  indivs <- hypatia:::create_individuals(states)

  pstates <- hypatia:::probabilities_of_states(dt, psq)

  E_I <- NULL

  p_E_I <- pstates$pgamma_E

  processes <- hypatia:::create_processes(
    indivs,
    states,
    pstates,
    psq,
    newpopulation,
    beta,
    E_I,
    numberof_days)

  out <- individual::simulate(
    indivs$human,
    processes,
    timestep
  )
  
  df <- data.frame(
     S = out$S,
     E = out$E,
     IMild = out$IMild,
     ICase1 = out$ICase1,
     ICase2 = out$ICase2,
     IOxGetLive1 = out$IOxGetLive1,
     IOxGetLive2 = out$IOxGetLive2,
     IOxNotGetLive1 = out$IOxNotGetLive1,
     IOxNotGetLive2 = out$IOxNotGetLive2,
     IOxGetDie1 = out$IOxGetDie1,
     IOxGetDie2 = out$IOxGetDie2,
     IOxNotGetDie1 = out$IOxNotGetDie1,
     IOxNotGetDie2 = out$IOxNotGetDie2,
     IMVGetLive1 = out$IMVGetLive1,
     IMVGetLive2 = out$IMVGetLive2,
     IMVNotGetLive1 = out$IMVNotGetLive1,
     IMVNotGetLive2 = out$IMVNotGetLive2,
     IMVGetDie1 = out$IMVNotGetLive2,
     IMVGetDie2 = out$IMVGetDie2,
     IMVNotGetDie1 = out$IMVNotGetDie1,
     IMVNotGetDie2 = out$IMVNotGetDie2,
     IRec1 = out$IRec1, IRec2 = out$IRec2,
     R = out$R, D = out$D, time = out$time, type = "Individual",
     legend = "Individual", stringsAsFactors = FALSE)
  
   # Check if df is a dataframe. If yes then turn it into a list
  numruns <- 0
  datapoints <- 0
  subtitle <- ""

  numdatapoints <- paste(length(df$time))
  numruns <- 1
  df <- list(df)
  subtitle <- paste(
    "Simulation for", numruns, "run and", numdatapoints, "data points")

  # Create group id for data
  df <- dplyr::bind_rows(df, .id = "group")

  #Convert to long format
  df <- tidyr::pivot_longer(tibble::as_tibble(df),
                            c("S", "E", "IMild", "ICase1", "ICase2",
                              "IOxGetLive1", "IOxGetLive2",
                              "IOxNotGetLive1", "IOxNotGetLive2", "IOxGetDie1",
                              "IOxGetDie2", "IOxNotGetDie1", "IOxNotGetDie2",
                              "IMVGetLive1", "IMVGetLive2", "IMVNotGetLive1",
                              "IMVNotGetLive2", "IMVGetDie1", "IMVGetDie2",
                              "IMVNotGetDie1", "IMVNotGetDie2", "IRec1",
                              "IRec2", "R", "D"))

  strname <- paste("SIR", df$type, "Model Simulation")

  ggplot2::ggplot(
    df, ggplot2::aes(x = df$time, y = df$value,
                     group = interaction(df$group, df$name), colour = df$name)) +
    ggplot2::geom_line(size = 0.5) +
    ggplot2::theme_bw() +
    ggplot2::labs(title = strname, subtitle = subtitle, color = df$legend) +
    ggplot2::labs(y = "States", x = "time") +
    ggplot2::theme(
      legend.justification = c("right", "top"),
      legend.box = c("horizontal", "vertical")
    ) +
    ggplot2::theme(
      text = ggplot2::element_text(color = "#444444", family = "Lucida Bright"),
      plot.title = ggplot2::element_text(size = 26, color = "#333333"),
      plot.subtitle = ggplot2::element_text(size = 13),
      axis.title.x = ggplot2::element_text(size = 16, color = "#333333"),
      axis.title.y = ggplot2::element_text(angle = 0, vjust = .5))

```


## License

MIT © Imperial College of Science, Technology and Medicine
